ODGI: scalable tools for pangenome graphs

### 2021-05-31 manuscript/main.tex
headers
2nd topic

    \subtitle{Genome Analysis}

    \title[ODGI: scalable tools for pangenome graphs]{ODGI: scalable tools for pangenome graphs}
    \author[Sample \textit{et~al}.]{
        Andrea Guarracino\,$^{\text{\sfb 1,}*}$,
        Simon Heumos\,$^{\text{\sfb 2}}$,
    % XXXXX,
        Pjotr~Prins\,$^{\text{\sfb 3}}$ and
        Erik~Garrison\,$^{\text{\sfb 3,}*}$
    }
    \address{$^{\text{\sf 1}}$Department, Institution, City, Post Code, Country \\
        $^{\text{\sf 2}}$Department, Institution, City, Post Code, Country \\
        $^{\text{\sf 3}}$Genetics Genomics \& Informatics, UTHSC, Memphis, TN, USA
    }

@@

    \topic{odgi viz, sort, drawn \& layout} by visualizing pangenome
    graphs, we can gain insight into the relationship between
    genomes. \cmd{odgi viz} applies binding and direct rendering to
    a raster image to generate a 1D representation able to scale up to
    gigabase pangenome graphs (Figure~1\vphantom{\ref{fig:1}}).
    However, pangenome graphs may present complex structures to
    visualize: \cmd{odgi sort} finds the best node order to simplify
    1D graph visualization by applying several cutting-edge sorting
    algorithms. \cmd{odgi drawn} extends the visualization in 2D,
    taking in input the layouts built by \cmd{odgi layout}.

>>>>

    \subtitle{Pangenome analysis}

    \title[ODGI: scalable tools for pangenome graphs]{ODGI: scalable tools for pangenome graphs}
    \author[Guarracino, Heumos \textit{et~al}.]{
        Andrea Guarracino\,$^{\text{\sfb 1,}*}$,
        Simon Heumos\,$^{\text{\sfb 2}}$,
    % XXXXX,
        Pjotr~Prins\,$^{\text{\sfb 3}}$ and
        Erik~Garrison\,$^{\text{\sfb 3,}*}$
    }
    \address{$^{\text{\sf 1}}$Department, Institution, City, Post Code, Country \\
        $^{\text{\sf 2}}$Department, Institution, City, Post Code, Country \\
        $^{\text{\sf 3}}$Genetics Genomics \& Informatics, UTHSC, Memphis, TN, USA
    }

@@

    \topic{odgi viz, sort, drawn \& layout} pangenome visualization is important to gain insight
    into the relationship between the embedded genomes. \cmd{odgi viz} generates a 1D representation
    able to scale up to gigabase pangenome graphs (Figure~1\vphantom{\ref{fig:1}}).
    \cmd{odgi sort} finds the best node order to simplify the graph visualization by applying several
    cutting-edge sorting algorithms. \cmd{odgi drawn} extends the visualization in 2D,
    taking in input the layouts built by \cmd{odgi layout}.
